### 2015-04-12 introduction.tex
Cleaning up first two sections

The advantage of moving to the BCC lattice is two fold. First, it's well known that the BCC lattice generates the optimal sampling pattern in $\realn^3$. The argument for optimality is simple; the sampling of a function with respect to the BCC lattice is equivalent to a periodization of it's frequency spectrum about the BCC's dual lattice, the \emph{Face Centered Cubic} (FCC) lattice. Optimality follows from the observation that the FCC lattice is the optimal sphere packing lattice in three dimensions, that is, it packs frequency replica as tightly as possible in the Fourier domain, resulting in less \emph{pre-aliasing} from sampling. For isotropically band-limited functions, this tighter packing of frequency content allows for about 30\% more information to be captured when compared to samplings generated from a Cartesian lattice. The second advantage to moving to the BCC lattice is that there exist reconstruction filters on the BCC lattice that outperform commonly used filters of equivalent order on the CC lattice in terms of both speed and accuracy \cite{practicalbox} (in software implementations) -- these filters are also more compact than their typical CC counterparts. In the context of our surface reconstruction scheme, this gives rise to regularization matrices that are more sparse on the BCC lattice and tend to provide faster convergence when optimizing the initial point set (\SC{sec:that-section-where-i-describe-this}.)

>>>>

The advantage of moving to the BCC lattice is two fold. First, it's well known that the BCC lattice generates the optimal sampling pattern in $\realn^3$. The argument for optimality is simple; the sampling of a function with respect to the BCC lattice is equivalent to a periodization of it's frequency spectrum about the BCC's dual lattice, the \emph{Face Centered Cubic} (FCC) lattice. Optimality follows from the observation that the FCC lattice is the optimal sphere packing lattice in three dimensions, that is, it packs frequency replica as tightly as possible in the Fourier domain, resulting in less \emph{pre-aliasing} from sampling. For isotropically band-limited functions, this tighter packing of frequency content allows for about 30\% more information to be captured when compared to samplings generated from a Cartesian lattice. The second advantage to moving to the BCC lattice is that there exist reconstruction filters on the BCC lattice that outperform commonly used filters of equivalent order on the CC lattice in terms of both speed and accuracy \cite{practicalbox} (in software implementations) -- these filters are also more compact than their typical CC counterparts. In the context of our surface reconstruction scheme, this gives rise to regularization matrices that are more sparse on the BCC lattice and tend to provide faster convergence when optimizing the initial point set (\SC{sec:vari_review}).

### 2015-04-12 poisson_errker.tex
Cleaning up first two sections

\section{Poisson's Equation} 
Before detailing how to specifically obtain an indicator function from the divergence of $\vec{V}(\vect{x})$, we discuss a general framework for solving Poisson's equation on a rectangular domain. We provide an analysis in $s$-dimensions, as this generalization comes at little cost. Explicitly, we seek an approximation of the function $\chi(\vect{x})$ that satisfies the Poisson equation with homogeneous Dirichlet boundary conditions, i.e. 
\begin{equation} \label{eq:PoissonEquation}
	\begin{split}
		\laplacian{\chi} &= f, \;\; \text{in} \;\; \oucube^s, \\
		\chi &= 0, \;\; \text{on} \;\; \partial \ucube^s,
	\end{split}
\end{equation}
where $\laplacian$ is the $s$-dimensional Laplace operator and
$\partial \ucube^s$ denotes the boundary of $\ucube^s$,
i.e. $\partial \ucube^s \cup \oucube^s = \ucube^s$.

>>>>

\section{Poisson's Equation} 
Before detailing how to obtain an indicator function from the divergence of $\vec{V}(\vect{x})$, we discuss a general framework for solving Poisson's equation on a rectangular domain. We provide an analysis in $s$-dimensions, as this generalization comes at little cost. Explicitly, we seek an approximation of the function $\chi(\vect{x})$ that satisfies the Poisson equation with homogeneous Dirichlet boundary conditions, i.e. 
\begin{equation} \label{eq:PoissonEquation}
	\begin{split}
		\laplacian{\chi} &= f, \;\; \text{in} \;\; \oucube^s, \\
		\chi &= 0, \;\; \text{on} \;\; \partial \ucube^s,
	\end{split}
\end{equation}
where $\laplacian$ is the $s$-dimensional Laplace operator and
$\partial \ucube^s$ denotes the boundary of $\ucube^s$,
i.e. $\partial \ucube^s \cup \oucube^s = \ucube^s$.

### 2015-04-12 relatedwork.tex
Cleaning up first two sections

Many surface reconstruction algorithms are so-called 
``\emph{implicit}'' reconstruction algorithms. They attempt to 
reconstruct an implicit function, $f : \realn^3 \mapsto \realn $, whose 
level-set, for some iso-value $s \in \realn$, $f(\mathbf{x})=s$ represents an
approximation to the original surface. Other non-implicit techniques
generally infer meshes through some other combinatorial means 
or set predefined logic/rules.

@@

Once, the smoothed gradient's divergence has been calculated, recovering the indicator
function is a simple matter of taking the inverse of the Laplacian over domain 
(i.e. solving the Poisson system). To do this, we take an approach that is also inspired 
by filtering methodologies in signal processing. In particular, we're interested in 
an approximate solution to Poisson?s equation that lies in a chosen shift-invariant 
space. Our solution methodology is reminiscent of the finite 
element method \cite{finite_el}. However, we do not impose any boundary 
conditions on the generating kernels. Rather, we satisfy homogeneous 
Dirichlet boundary conditions implicitly by requiring that the coefficient sequence be odd 
(Section III). The solution is obtained by applying a digital filter to point samples. 
We approach the problem from first principles and derive the tools necessary 
to design solution filters for a chosen shift-invariant space (\SC{sec:recoveringX}).
\ednote{I still need to fix-up section refs/refs here.}

>>>>

Many surface reconstruction algorithms are so-called ``\emph{implicit}'' reconstruction algorithms. They attempt to 
reconstruct an implicit function, $f : \realn^3 \mapsto \realn $, whose level-set, for some iso-value $s \in \realn$, $f(\vect{x})=s$ represents an approximation to the original surface. Other non-implicit techniques generally infer meshes through some other combinatorial means or set predefined logic/rules.

@@

Once, the smoothed gradient's divergence has been calculated, recovering the indicator function is a simple matter of taking the inverse of the Laplacian over domain (i.e. solving the Poisson system). To do this, we take an approach that is also inspired by filtering methodologies in signal processing. In particular, we're interested in an approximate solution to Poisson?s equation that lies in a chosen shift-invariant space. Our solution methodology is reminiscent of the finite element method. However, we do not impose any boundary conditions on the generating kernels. Rather, we satisfy homogeneous Dirichlet boundary conditions implicitly by requiring that the coefficient sequence be odd (Section III). The solution is obtained by applying a digital filter to point samples. We approach the problem from first principles and derive the tools necessary to design solution filters for a chosen shift-invariant space (\SC{sec:recoveringX}).

### 2015-04-12 results.tex
Cleaning up first two sections

We now turn to the problem of designing filters that discretize the operator
$\ftpairs{\invlaplacian}{(-4\pi^2(\omega_1^2 +
  \omega_2^2))^{-1}}$, and
are to be used in conjunction with the tensor-product B-splines. Recall that the
space $\aspace{\ints^2_h}{\tpbs^k}$ generated by $\tpbs^k(x_1,x_2) =
\cbs^{k}(x_1)\cbs^{k}(x_2)$ (where $\cbs^k$ is as defined
in~\EQ{eq:1DBspline}), satisfies the approximation property:
$\order{\ints^2}{\tpbs^k}=k+1$. This result also extends to the Cartesian lattice in
higher dimensions. Consequently, we cover the 2D case in detail here. The
extension to 3D is left to the reader.

\paragraph{Interpolation}
For the generator $\tpbs^k$, we are interested in a $(k+1)$-th order
asymptotically optimal discretization of the inverse Laplacian
$\invlaplacian$. According to Proposition~\ref{prop:1}, we need the
two filters $p_{\tpbs^k}$ and $\lambda$.

Since $\tpbs^k$ is a compact generator, $p_{\tpbs^k}$ will also be a compact
filter. Furthermore, since $\tpbs^k$ is separable, $p_{\tpbs^k}$ can be
determined by sampling $\cbs^k(x)$ to yield the filter $p_{\cbs^k}[n] =
\cbs^k(n)$ where $n \in \ints$. The weights of $p_{\tpbs^k}$ are then obtained
by a simple tensor product, i.e. $p_{\tpbs^k}[n_1,n_2] =
p_{\cbs^k}[n_1]p_{\cbs^k}[n_2] \ftpairs{}{} \ft{P}_{\tpbs^k}(\omega_1,\omega_2)
= \ft{P}_{\cbs^k}(\omega_1)\ft{P}_{\cbs^k}(\omega_2)$.

>>>>

We now turn to the problem of designing filters that discretize the operator 
$\ftpairs{\invlaplacian}{(-4\pi^2(\omega_1^2 +\omega_2^2))^{-1}}$, and are to be used in conjunction with the tensor-product B-splines. For the generator $M_{\Xii_{C4}}$, we are interested in a $4$-th order asymptotically optimal discretization of the inverse Laplacian $\invlaplacian$. According to Proposition~\ref{prop:1}, we need the two filters $p_{M_{\Xii_{C4}}}$ and $\lambda$.

Since $M_{\Xii_{C4}}$ is a compact generator, $p_{M_{\Xii_{C4}}^k}$ will also be a compact filter. Furthermore, since $\tpbs^k$ is separable, $p_{\tpbs^k}$ can be
determined by sampling $\cbs^k(x)$ to yield the filter $p_{\cbs^k}[n] =
\cbs^k(n)$ where $n \in \ints$. The weights of $p_{M_{\Xii_{C4}}}$ are then obtained
by a simple tensor product, i.e. $p_{M_{\Xii_{C4}}^k}[n_1,n_2,n_3] =
p_{\cbs^k}[n_1]p_{\cbs^k}[n_2] \ftpairs{}{} \ft{P}_{\tpbs^k}(\omega_1,\omega_2,\omega_3) = \ft{P}_{\cbs^k}(\omega_1)\ft{P}_{\cbs^k}(\omega_2)\ft{P}_{\cbs^k}(\omega_3)$.
